%-------------------------
% Resume in Latex
% Author : Jian Liew
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    % \textbf{#1}{: #2 \vspace{-2pt}}
    {#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://jianliew.me/}{\Large Jian Loong Liew}} & Email : \href{mailto:jianloongliew@gmail.com}{jianloongliew@gmail.com}\\
  \href{https://www.github.com/JianLoong}{https://www.github.com/JianLoong} & Mobile : +61-4-3117-0997 \\
\end{tabular*}

\vspace{+4pt}
Test


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Monash University}{Melbourne, Australia}
      {Master of Information Technology (Professional) - Thesis}{Aug. 2013 -- Aug. 2015}
      \resumeItemListStart
        \resumeItem{}{Faculty of Information Technology Merit Scholarship}
        \resumeItem{}{Completed thesis titled "Category R-tree", a data structure for optimised spatial queries.}
        \resumeItem{Relevant Units - }{Mobile and Distributed Systems, Data Analysis \& Processing}
      \resumeItemListEnd
    \resumeSubheading
      {Swinburne University of Technology}{Melbourne, Australia}
      {Bachelor of Science (Computer Science \& Software Engineering);  GPA: 3.91}{Jul. 2010 -- Dec. 2012}
      \resumeItemListStart
        \resumeItem{}{Swinburne University of Technology Merit Scholarship}
        \resumeItem{}{Won Corporate and Industry Award by obtaining the highest cGPA in the course.}
        \resumeItem{Relevant Units - }{System Architecture \& Design, Software Engineering Project}
      
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Monash University}{Melbourne, Australia}
      {Sessional Lecturer \& Teaching Associate}{Oct 2015 - Present}
      \newline
      \resumeItemListStart
        \resumeItem{\textbf{FIT9131 - Programming Foundations in Java.}}
        {Lectured for Semester 2, 2018}
        \resumeItem{\textbf{Subjects taught include - }}{FIT9134 - Computer Architecture \& Operating Systems,
         FIT9135 - Data Communications, 
         FIT5042 - Enterprise Application Development, 
         FIT5136 - Software Engineering}       
      \resumeItemListEnd
    \resumeSubheading
      {Sisuwellness}{Melbourne, Australia}
      {Android Developer}{Jan 2014 - Oct 2016}
      \resumeItemListStart
        \resumeItem{Push Notifications - }
          {Created Push Notifications features using \textbf{Google Firebase}}
        \resumeItem{Material Design - }
          {Bulk data processing and injection service from Hadoop to Cassandra and provides a thin REST layer on top for serving offline computed data online.}
        \resumeItem{Workflows}
          {Dataduct an open source workflow framework to create and manage data pipelines leveraging reusables patterns to expedite developer productivity.}
        \resumeItem{Data Collection}
          {Designed the internal survey and crowd sourcing platform which allowed for creating various tasks for crowd sourcing or embedding surveys across the Coursera platform.}
        \resumeItem{Dev Environment}
          {Analytics environment based on docker and AWS, standardized the python and R dependencies. Wrote the core libraries that are shared by all data scientists.}
        \resumeItem{Data Warehousing}
          {Setup, schema design and management of Amazon Redshift. Built an internal app for access to the data using a web interface. Dataduct integration for daily ETL injection into Redshift.}
        \resumeItem{Recommendations}
          {Core service for all recommendation systems at Coursera, currently used on the homepage and throughout the content discovery process. Worked on both offline training and online serving.}
        \resumeItem{Content Discovery}
          {Improved content discovery by building a new onboarding experience on coursera. Using this to personalize the search and browse experience. Also worked on ranking and indexing improvements.}
        \resumeItem{Course Dashboards}
          {Instructor dashboards and learner surveying tools, which helped instructors run their class better by providing data on Assignments and Learner Activity.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{QuantSoftware Toolkit}
%       {Open source python library for financial data analysis and machine learning for finance.}
%     \resumeSubItem{Github Visualization}
%       {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%     \resumeSubItem{Recommendation System}
%       {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%   \resumeSubHeadingListEnd

%
% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Java, Python, JavaScript, C, C++, C\#, SQL, PHP, Shell Scripting}     
   }
   \item{
    \textbf{Technologies}{: Data Warehousing, Git, RESTful Web Service}
   }
 \resumeSubHeadingListEnd

 \section{Visa Status}
 \textbf{Permanent Resident} - Skilled - Independent (subclass 189)


%-------------------------------------------
\end{document}
